---
title: "Statistical Analysis Report"
date: 'Date: `r Sys.Date()`'
author: "_via Hatfield & Hogg's Text Analysis App_"
format: docx
execute: 
  warning: false
  error: false
  message: false
  echo: false
params:
  report_rv: ""
  stats_report_rv: ""
always_allow_html: true
---

```{r}
#| echo: false
#| message: false
#| warning: false
#| error: false
if(!require('pacman'))install.packages('pacman')
library(pacman)

pacman::p_load(
  dplyr,    flextable,
  ggplot2, kableExtra,
  knitr, readr,
  stringr, tidyr
  )

knitr::opts_chunk$set(fig.align = 'center',
               fig.width = 7,
               fig.height = 4)

```

```{r}
#| echo: false
#| warning: false

# Setting defaults to render where parts missing, e.g. user downloads report with nothing uploaded
counts_subtitle <- ""
summary_stats_subtitle <- ""
num_stops <- 0
num_files <- 0

# Summary stats 
if(!is.null(params$report_rv$num_files)){
  num_files <- params$report_rv$num_files
}

# Creating variable for number of stop-words that were included.
if(!is.null(params$report_rv$stop_words_final)){
  num_stops <- nrow(params$report_rv$stop_words_final)
} 

# Creating summary stats values
if(!is.null(params$report_rv$content_tf_idf)){
    total_tokens <- params$report_rv$content_tf_idf$`Corpus token count`[1]
  mean_token_count <- params$report_rv$content_tf_idf$`Mean token count`[1]
  sd_token_count <- c(sd(params$report_rv$content_tf_idf$`Token Count`))
  
  summary_stats_subtitle <-  paste("The total count of all tokens in the corpus was ", total_tokens,
                                   ". The mean token count per document was ", 
                            mean_token_count, 
                            " with a standard deviation of ", 
                            round(sd_token_count, 2), ".",
                          collapse = ",")
  
  max_min_token <- params$report_rv$content_tf_idf %>%
    arrange(desc(`Token Count`)) %>%
    select(ID,`Token Count`)
  highest_token_count <- slice_head(max_min_token)
  lowest_token_count <- slice_tail(max_min_token)
  
  highest_count <- highest_token_count[1,2]
  highest_doc <- highest_token_count[1,1]
  lowest_count <- lowest_token_count[1,2]
  lowest_doc <- lowest_token_count[1,1]
  
  counts_subtitle <-  paste("The document with the highest token count (", highest_count, ") was ", 
                            highest_doc, 
                            ". The document with the lowest token count (", lowest_count, ") was ", 
                            lowest_doc, ".",
                          collapse = ",")
}
```

---

## Corpus summary statistics

A corpus consisting of `r num_files` documents was submitted for analysis. A total of `r num_stops` stop-words were omitted from their contents.

`r summary_stats_subtitle`
`r counts_subtitle`

\

```{r}
#| echo: false
#| warning: false

data <- params$report_rv$content_tf_idf
if(!is.null(data)){
  summary <- tibble(`Mean document token count` = 
                    mean_token_count, 
                  `Std. dev.` = c(sd(data$`Token Count`)),
                  `Min.` = min(data$`Token Count`), 
                  `Max.` = max(data$`Token Count`), 
                  `Total corpus tokens` = total_tokens
                  )

  flextable(summary, cwidth = 2) %>% 
    set_caption(caption =  "Table 1. Summary statistics for the current corpus.") %>% 
    # font(fontname = "Calibri (Body)", part = "all") %>%
    # fontsize(size = 10, part = "body") %>%
    # theme_booktabs() %>% # default theme
    autofit()
}
```

<!-- Correlation matrix -->

```{r}
#| echo: false
#| warning: false
#| error: false
correlation_title <- ""
correlation_blurb <- ""

if(!is.null(params$stats_report_rv$corr_plot_non_plotly)){
  correlation_title <- "Correlation Matrix Heat-map"
  correlation_blurb <- "Below shows a correlation heat-map between variables within the selected dataset."
}
```

## `r correlation_title`

`r correlation_blurb`

```{r}
#| echo: false
#| warning: false
#| error: false

if(!is.null(params$stats_report_rv$corr_plot_non_plotly)){
  params$stats_report_rv$corr_plot_non_plotly
}
```

```{r regression}
#| echo: false
#| warning: false
#| error: false

reg_title <- ""
reg_blurb <-  ""
formula <- ""

if(!is.null(params$stats_report_rv$formula_reg)){
  reg_title <- "Regression analysis"
  reg_blurb <- "The following outlines the regression formula and summary of the model fitted."
  formula <-  paste("The specified regression formula was:",
                     params$stats_report_rv$formula_reg, ".",
                    collapse = ",")
}

```

## `r reg_title`

`r reg_blurb`

`r formula`

```{r}
#| echo: false
#| warning: false
#| error: false

if(!is.null(params$stats_report_rv$reg_summary_raw)){
  params$stats_report_rv$reg_summary_raw
}
```


```{r}
#| echo: false
#| warning: false
#| error: false
resid_title <- ""
resid_blurb <- ""
resid_plots <- ""

if(!is.null(params$stats_report_rv$residual_plots)){
  resid_title <- "Residual Plots"
  resid_blurb <- "The residual plots for the fitted regression model are shown below."
  resid_plots <- params$stats_report_rv$residual_plots
}

```

### `r resid_title`

`r resid_blurb`

```{r}
#| echo: false
#| warning: false
#| error: false
if(!is.null(params$stats_report_rv$residual_plots)){
  params$stats_report_rv$residual_plots
}
```

```{r}
#| echo: false
#| warning: false
#| error: false

# Statistical test headers/blurbs

stats_tests_title <- ""
# If not any (none) of the statistical tests are null, 
# render statistical test title
if(!any(is.null(c(params$stats_report_rv$anova_table, 
                  params$stats_report_rv$ttest_table, 
                  params$stats_report_rv$chisq_res)))
   ){
  stats_tests_title <- "Statistical Tests"
}

```

```{r}
#| echo: false
#| warning: false
#| error: false

# ANOVA test headers/blurbs
anova_title <- ""
anova_blurb <- ""

if(!is.null(params$stats_report_rv$anova_table)){
  anova_title <- "Analysis of variances (ANOVA)"
  anova_blurb <- "An ANOVA was used to test for any  significant differences between means of three or more independent groups. A summary of the ANOVA test results for the fitted model are shown below."
}

```

## `r stats_tests_title`

### `r anova_title`

`r anova_blurb`

```{r}
#| echo: false
#| warning: false
#| error: false
if(!is.null(params$stats_report_rv$anova_table)){
  params$stats_report_rv$anova_table
}
```


```{r}
#| echo: false
#| warning: false
#| error: false

# t-test headers/blurbs/results
ttest_title <- ""
ttest_blurb <- ""


if(!is.null(params$stats_report_rv$ttest_res)){
  ttest_title <- "T-test"
  ttest_blurb <- "A t-test was performed to determine if there was a significant difference in the means of two independent groups being compared. A summary of the t-test results on the fitted model are shown below."
}

```

### `r ttest_title`

`r ttest_blurb`

```{r}
#| echo: false
#| warning: false
#| error: false
if(!is.null(params$stats_report_rv$ttest_res)){
  params$stats_report_rv$ttest_res
}
```


```{r}
#| echo: false
#| warning: false
#| error: false

# chi-sq test headers/blurbs/results
chi_sq_title <- ""
chi_sq_blurb <- ""

if(!is.null(params$stats_report_rv$chisq_res)){
  chi_sq_title <- "Chi-squared test"
  chi_sq_blurb <- "A chi-squared test was used to determine for a significant association between two categorical variables. The results of the chi-squared test for the fitted model are shown below."
}
```

### `r chi_sq_title`

`r chi_sq_blurb`

```{r}
#| echo: false
#| warning: false
#| error: false

if(!is.null(params$stats_report_rv$chisq_res)){
  params$stats_report_rv$chisq_res
}
```

